\section{Human participants}
We will be running a user study to evaluate our simulator, so we will need to get approval from Imperial College London's Science, Engineering and Technology Research Ethics Committee (\textbf{SETREC}). This process can take some time, so we will need to start this process after the submission of this interim report to ensure we have approval by the spring term when the user study is expected to take place. 

\section{Data collection}
We will be collecting data from the user study, so we will need to ensure that we comply with the General Data Protection Regulation (\textbf{GDPR}). We will need to ensure that we have a data protection impact assessment (\textbf{DPIA}) and that we have a data management plan (\textbf{DMP}). Furthermore, we will also need to ensure that we have consent from the participants to collect their data and reuse it.

\section{Military applications}
This technology in theory could be used for military applications, however, we believe is unlikely to be used for such purposes, and if it was, it would not be directly used in combat and would not be more dangerous than other existing technologies.

\section{Copywrite Limitations}
\subsection{Open Source}
We will be using the Azure Kinect SDK which is licensed under the MIT license. We will also be using the Nix package manager which is licensed under the LGPL-2.1 license. Furthermore, we will also be using the Nixpkgs repository which is licensed under the MIT license. We will also be using the \texttt{dlib} library which is licensed under the Boost Software License 1.0 (BSL-1.0). We will also be using the OpenGL library which is licensed under the open-source license for the use of sample Implementation (SI). Furthermore, we will also be using the GLFW library which is licensed under the zlib license. We will also be using the GLM library which is licensed under the MIT license. We will also be using the OpenCV license under the Apache License. 
\subsection{Proprietary}
Furthermore, we use Microsoft's proprietary depth engine designed to work with the Azure Kinect SDK which is not open source.