\documentclass[12pt,twoside]{report}

% some definitions for the title page
\newcommand{\reporttitle}{A Virtual Volumetric Screen}
\newcommand{\reportauthor}{Robert Buxton}
\newcommand{\supervisor}{Dr Nicole Salomons}
\newcommand{\reporttype}{MEng Individual Project}
\newcommand{\degreetype}{Computing MEng}  

% load some definitions and default packages
\input{inputs/includes}

% load some macros
\input{inputs/notation}

% load title page
\begin{document}
\include{title/titlepage}


% page numbering etc.
\pagenumbering{roman}
\clearpage{\pagestyle{empty}\cleardoublepage}
\setcounter{page}{1}
\pagestyle{fancy}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
	This thesis presents the development of a virtual volumetric screen designed to simulate volumetric displays for Human-Computer Interaction (HCI) research. The primary objective is to create a cost-effective, reproducible, and simple system that enables researchers to explore the usability of volumetric displays without requiring access to expensive and specialized hardware. The system employs head and hand tracking to render 3D content on a standard 2D monitor, creating the illusion of depth and allowing natural interaction with virtual objects. \\
	
	A comprehensive user study was conducted to evaluate the effectiveness of the system. The study compared user performance in tasks requiring spatial interaction under different conditions: 3D versus 2D views and direct hand interaction versus teleoperation. The results showed a significant improvement in task performance when using a 3D view with direct hand interaction, highlighting the importance of intuitive and immersive interaction modes in volumetric display research. \\
	
	Future work includes expanding the system's compatibility with different hardware and operating systems, improving hand tracking accuracy, and exploring multi-user support. 
\end{abstract}

% \cleardoublepage
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
I would like to thank \textbf{in order of importance}:
\begin{itemize}[noitemsep]
	% \item ChatGPT
    \item My supervisor Dr Nicole Salomons for her guidance and support throughout this project so far.
    \item My loving family who still think I am studying physics (\textbf{Mabel}) for some reason.
\end{itemize}
\clearpage{\pagestyle{empty}\clearpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%--- table of contents
\fancyhead[RE,LO]{\sffamily {Table of Contents}}
\tableofcontents


\clearpage{\pagestyle{empty}\clearpage}
\pagenumbering{arabic}
\setcounter{page}{1}
\fancyhead[LE,RO]{\slshape \rightmark}
\fancyhead[LO,RE]{\slshape \leftmark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\include{introduction/introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Ethical Discussion}
\include{ethics/ethics}
\label{sect:ethics}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Background}
\include{background/3d}
\label{sect:3d}
\include{background/nix}
\label{sect:nix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Methods}
\include{methods/projection}
\label{sect:projection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
\include{implementation/overview}
\label{sect:overview}
\include{implementation/buildsystem}
\label{sect:buildsystem}
\include{implementation/renderer}
\label{sect:renderer}
\include{implementation/tracker}
\label{sect:tracker}
\include{implementation/userstudy}
\label{sect:userstudy}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Evaluation}
\include{evaluation/volsim} 
\label{sect:eval-volsim}
\include{evaluation/userstudy}
\label{sect:eval-userstudy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Future Work, Conclusions and Contributions}
\include{conclusions/conclusions}
\label{sect:conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\printbibliography

\appendix
\chapter{Final Package}
\label{app:final-package}
\include{appendix/output}
\chapter{Survey Forms}
\label{app:survey}
\include{appendix/forms}
\chapter{Extended User Study Results}
\label{app:results}
\include{appendix/graphs}
\end{document}