\section{Simulator Evaluation}

\subsection{Overall System}
\begin{enumerate}
	\item It works on other machines first run, (different machine different gpu). Verify it works on WSL?
\end{enumerate}

\subsection{Tracking System}
\subsubsection{Together}
\begin{enumerate}
	\item Draw a bell curve of latency. Don't forget to factor in the latency built into the camera. 
	\item Justify the downscaling, show that it's slow with no upscaling and downscaling even more offers negligible speed increases.  
	\item Mention lighting issues.
\end{enumerate}

\subsubsection{Head Tracking}
\begin{enumerate}
	\item Estimate throughput via logging (unique points). Draw a bell curve like graph of the time between each result from the tracker.
	\item Measure accuracy by moving head around and seeing how often it loses track at different distances. While facing camera. Test with glasses on?
	\item Measure the angle of the head where the tracker stops working.  
\end{enumerate}

\subsubsection{Hand tracking}
\begin{enumerate}
	\item Estimate throughput via logging (unique points). Draw a bell curve like graph of the time between each result from the tracker.
	\item Measure accuracy by moving head around and seeing how often it loses track at different distances. Change hand orientations
	\item Mention occlusion issue. 
	\item Wall vs no wall issue. 
	\item The colour of the screen also affects the hand tracker. 
\end{enumerate}

\subsection{Renderer}
\begin{enumerate}
	\item Reconstruct real life item, compare photos of item from different angles. 
	\item Get framerate?
\end{enumerate}